---
title: "Real Data Reproducibility Workflow"
output:
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# Overview

This file summarizes the face-data scripts, saved result files, and plotting scripts used for the real data figures in the manuscript.

The first sections check the saved result files in `real data/results/`. Commands for rerunning the real data analyses are listed near the end of the file.

# Directory setup

Knit this file from the root of the reproducibility folder, the same folder that contains `Readme.md`, `simulation/`, and `real data/`.

```{r directories}
root_dir <- normalizePath(".", winslash = "/", mustWork = TRUE)
real_code <- file.path(root_dir, "real data", "code")
real_plot <- file.path(root_dir, "real data", "plot")
real_results <- file.path(root_dir, "real data", "results")

stopifnot(
  dir.exists(real_code),
  dir.exists(real_plot),
  dir.exists(real_results)
)

data.frame(
  component = c("real data code", "real data plot scripts", "saved real data results"),
  path = c(real_code, real_plot, real_results)
)
```

# Package requirements

The result-file checks below use base R only. Running the real data and plotting scripts may require the following packages:

- Core computation: `parallel`, `pbapply`, `igraph`, `Matrix`, `matrixStats`.
- Face data input: `R.matlab`.
- Spherical Frechet regression: `Directional`, `Riemann`, `spherepc`.
- Plotting: `ggplot2`, `ggpubr`, `plot3D`.

# Saved result inventory

Saved CSV files in `real data/results/`:

```{r saved-realdata-results}
realdata_csv <- sort(list.files(real_results, pattern = "\\.csv$", full.names = FALSE))
data.frame(file = realdata_csv)
```

# Workflow map

```{r realdata-map}
realdata_map <- data.frame(
  manuscript_output = c(
    "Figure 5",
    "Figure 6",
    "Figure 7",
    "Figure 8, left",
    "Figure 8, right",
    "Figure S.14",
    "Figure S.15, left",
    "Figure S.15, right"
  ),
  existing_script = c(
    "real data/code/Real data_face.R",
    "real data/plot/plot_sphere.R",
    "real data/code/Real data_noise face.R",
    "real data/plot/plot_noise.R",
    "real data/plot/plot_noise.R",
    "real data/plot/plot_box.R",
    "real data/plot/plot_noise.R",
    "real data/plot/plot_noise.R"
  ),
  settings_or_inputs = c(
    "Representative face images selected in the face data script",
    "Predicted sphere points from a single run",
    "Noise-contaminated face image examples",
    "n1=70, ratios=seq(0, 1, 0.2), noise_sd=0.3, localized contamination",
    "n1=70, ratios=seq(0, 0.3, 0.06), whole-image noise level",
    "n1=70 and n1=140 original face data summaries",
    "n1=140, ratios=seq(0, 1, 0.2), noise_sd=0.3, localized contamination",
    "n1=140, ratios=seq(0, 0.3, 0.06), whole-image noise level"
  ),
  saved_result = c(
    NA,
    NA,
    NA,
    "real data_noise_ratio_70.csv",
    "real data_noise_degree_70.csv",
    "real data_face_70label_sphere.csv; real data_face_140label_sphere.csv; corresponding _lr and _ud files",
    "real data_noise_ratio_140.csv",
    "real data_noise_degree_140.csv"
  ),
  stringsAsFactors = FALSE
)

realdata_map
```

# Original face data summaries

The original face analysis compares four methods in the following column order: `naive-knn`, `semi-knn`, `naive-nw`, `semi-nw`. The saved files contain 100 repetitions. The table below recomputes the reported averages from the saved CSV files.

```{r original-face-summary}
method_names <- c("naive-knn", "semi-knn", "naive-nw", "semi-nw")

summarize_face_file <- function(filename, metric, n_label) {
  dat <- read.csv(file.path(real_results, filename), check.names = FALSE)
  values <- colMeans(dat[, c("V1", "V2", "V3", "V4")])
  data.frame(
    n_label = n_label,
    metric = metric,
    method = method_names,
    mean = as.numeric(values),
    row.names = NULL
  )
}

face_summary <- rbind(
  summarize_face_file("real data_face_70label_sphere.csv", "spherical geodesic MSE", 70),
  summarize_face_file("real data_face_70label_sphere_lr.csv", "left-right MAE in degrees", 70),
  summarize_face_file("real data_face_70label_sphere_ud.csv", "up-down MAE in degrees", 70),
  summarize_face_file("real data_face_140label_sphere.csv", "spherical geodesic MSE", 140),
  summarize_face_file("real data_face_140label_sphere_lr.csv", "left-right MAE in degrees", 140),
  summarize_face_file("real data_face_140label_sphere_ud.csv", "up-down MAE in degrees", 140)
)

face_summary$mean <- round(face_summary$mean, 3)
face_summary
```

# Noisy face data summaries

The noisy face analysis uses saved CSV files for contamination proportion and noise level. The table below summarizes the saved results.

```{r noisy-face-summary}
noise_files <- c(
  "real data_noise_ratio_70.csv",
  "real data_noise_degree_70.csv",
  "real data_noise_ratio_140.csv",
  "real data_noise_degree_140.csv"
)

summarize_noise_file <- function(filename) {
  dat <- read.csv(file.path(real_results, filename), check.names = FALSE)
  values <- colMeans(dat[, c("V1", "V2", "V3", "V4")])
  data.frame(
    file = filename,
    method = method_names,
    mean_over_grid = round(as.numeric(values), 3),
    stringsAsFactors = FALSE
  )
}

do.call(rbind, lapply(noise_files, summarize_noise_file))
```

# Regenerating figures from saved result files

The plotting scripts in `real data/plot/` read saved result files and write figure files using the manuscript plotting style. If a plotting script contains a filename near the top of the file, set it to the target CSV before sourcing the script.

```{r regenerate-realdata-plots, eval=FALSE}
old_dir <- getwd()

# plot_box.R: boxplots for Figure S.14.
setwd(real_results)
source(file.path(real_plot, "plot_box.R"))

# plot_noise.R: noise-contamination and noise-level curves for Figure 8 and Figure S.15.
setwd(real_results)
source(file.path(real_plot, "plot_noise.R"))

# plot_sphere.R: sphere visualizations for Figure 6.
# This script uses objects created by a single run of Real data_face.R.

setwd(old_dir)
```

# Rerunning real data analyses

The following chunks are set to `eval=FALSE` because the analyses use parallel computation and may take substantial time. Before running them, check the intended values of parameters such as `n1` and `ratios`.

```{r rerun-original-face-analysis, eval=FALSE}
old_dir <- getwd()
setwd(real_code)

# Real data_face.R runs the original face-data analysis for Figures 5, 6, and S.14.
source("Real data_face.R")

setwd(old_dir)
```

```{r rerun-noisy-face-analysis, eval=FALSE}
old_dir <- getwd()
setwd(real_code)

# Real data_noise face.R runs the noisy-face analysis for Figures 7, 8, and S.15.
source("Real data_noise face.R")

setwd(old_dir)
```

# Session information

The saved real data results were generated using R version 4.5.0. The following output records the R environment used to render this document.

```{r session-info}
sessionInfo()
```
