---
title: "Simulation Reproducibility Workflow"
output:
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# Overview

This file summarizes the simulation scripts, saved result files, and plotting scripts used for the simulation figures in the manuscript "Efficient Semi-supervised Frechet Regression with Low-dimensional Manifold Structures".

The first sections check the saved CSV files in `simulation/results/`. Commands for rerunning the experiments are listed near the end of the file.

# Directory setup

Knit this file from the root of the reproducibility folder, the same folder that contains `Readme.md`, `simulation/`, and `real data/`.

```{r directories}
root_dir <- normalizePath(".", winslash = "/", mustWork = TRUE)
sim_code <- file.path(root_dir, "simulation", "code")
sim_plot <- file.path(root_dir, "simulation", "plot")
sim_results <- file.path(root_dir, "simulation", "results")

stopifnot(
  dir.exists(sim_code),
  dir.exists(sim_plot),
  dir.exists(sim_results)
)

data.frame(
  component = c("simulation code", "simulation plot scripts", "saved simulation results"),
  path = c(sim_code, sim_plot, sim_results)
)
```

# Package requirements

The result-file checks below use base R only. Running the simulation and plotting scripts may require the following packages:

- Core computation: `parallel`, `pbapply`, `igraph`, `Matrix`, `matrixStats`.
- SPD response simulations: `shapes`, `RiemBase`, `tmvtnorm`.
- Spherical response simulations: `Directional`, `Riemann`, `spherepc`, `tmvtnorm`.
- Radius experiments: `FNN`, `pracma`.
- Plotting: `ggplot2`, `scatterplot3d`.

# Saved result inventory

Saved CSV files in `simulation/results/`:

```{r saved-simulation-results}
simulation_csv <- sort(list.files(sim_results, pattern = "\\.csv$", full.names = FALSE))
data.frame(file = simulation_csv)
```

# Main-text simulation figures

The table links the main-text figures to the saved result files and the scripts/settings that generated them.

```{r main-simulation-map}
main_simulation_map <- data.frame(
  figure = c(
    "Figure 1",
    "Figure 2(a)",
    "Figure 2(b)",
    "Figure 2(c)",
    "Figure 2(d)",
    "Figure 3(a)",
    "Figure 3(b)",
    "Figure 3(c)",
    "Figure 3(d)",
    "Figure 4(a)",
    "Figure 4(b)",
    "Figure 4(c)",
    "Figure 4(d)"
  ),
  existing_script = c(
    "simulation/plot/plot_swiss roll.R",
    rep("simulation/code/main_spd.R", 4),
    rep("simulation/code/main_spd.R", 4),
    "simulation/code/radius_spd.R",
    "simulation/code/rate_spd.R",
    "simulation/code/main_spd.R",
    "simulation/code/curve_spd.R"
  ),
  settings = c(
    "Swiss roll illustration",
    'scenario="Swiss", setting=1, snr=2, method="LogEuclidean", n1=100, NN=8000, n3=1000',
    'scenario="Swiss", setting=1, snr=4, method="LogEuclidean", n1=100, NN=8000, n3=1000',
    'scenario="Swiss", setting=2, snr=2, method="LogEuclidean", n1=100, NN=8000, n3=1000',
    'scenario="Swiss", setting=2, snr=4, method="LogEuclidean", n1=100, NN=8000, n3=1000',
    'scenario="Swiss2", setting=1, snr=2, method="LogEuclidean", n1=200, NN=8000, n3=1000',
    'scenario="Swiss2", setting=1, snr=4, method="LogEuclidean", n1=200, NN=8000, n3=1000',
    'scenario="Swiss2", setting=2, snr=2, method="LogEuclidean", n1=200, NN=8000, n3=1000',
    'scenario="Swiss2", setting=2, snr=4, method="LogEuclidean", n1=200, NN=8000, n3=1000',
    'scenario="Swiss2", setting=1, snr=2, method="LogEuclidean", n1=200, n2=3000, n3=1000',
    'scenario="Swiss2", setting=4, snr=2, method="LogEuclidean", unlabeled n1=3000, labeled NN=1500, n3=1000',
    'scenario="Swiss5", setting=3, snr=2, method="LogEuclidean", n1=200, NN=8000, n3=1000',
    'Curve setting, snr=2, n1=100, NN=8000, n3=1000'
  ),
  saved_result = c(
    NA,
    "spd-100-8000-1000-Swiss-setting1-snr_2.csv",
    "spd-100-8000-1000-Swiss-setting1-snr_4.csv",
    "spd-100-8000-1000-Swiss-setting2-snr_2.csv",
    "spd-100-8000-1000-Swiss-setting2-snr_4.csv",
    "spd-200-8000-1000-Swiss2-setting1-snr_2.csv",
    "spd-200-8000-1000-Swiss2-setting1-snr_4.csv",
    "spd-200-8000-1000-Swiss2-setting2-snr_2.csv",
    "spd-200-8000-1000-Swiss2-setting2-snr_4.csv",
    "spd-200-3000-1000-Swiss2-setting1_snr_2_r_impaction.csv",
    "spd-1200-3000-1000-Swiss2-setting4-snr_2_rate.csv",
    "spd-200-8000-1000-Swiss5-setting3-snr_2.csv",
    "spd-100-8000-1000-Curve-snr_2.csv"
  ),
  stringsAsFactors = FALSE
)

main_simulation_map
```

# Supplementary simulation figures

```{r supplementary-simulation-map}
supplementary_simulation_map <- data.frame(
  figure = c(
    "Figure S.1(a)", "Figure S.1(b)",
    "Figure S.2(a)", "Figure S.2(b)",
    "Figure S.3(a)", "Figure S.3(b)",
    "Figure S.4(a)", "Figure S.4(b)",
    "Figure S.5(a)", "Figure S.5(b)",
    "Figure S.6",
    "Figure S.7",
    "Figure S.8",
    "Figure S.9(a)", "Figure S.9(b)",
    "Figure S.10(a)", "Figure S.10(b)",
    "Figure S.11(a)", "Figure S.11(b)",
    "Figure S.12(a)", "Figure S.12(b)",
    "Figure S.13(a)", "Figure S.13(b)"
  ),
  existing_script = c(
    "simulation/code/main_spd.R", "simulation/code/main_sphere.R",
    "simulation/code/main_spd.R", "simulation/code/main_sphere.R",
    "simulation/code/main_spd.R", "simulation/code/main_spd.R",
    "simulation/code/main_spd.R", "simulation/code/main_spd.R",
    "simulation/code/radius_spd.R", "simulation/code/radius_sphere.R",
    "simulation/code/rate_spd.R",
    "simulation/code/rate_sphere.R",
    "simulation/code/rate_spd.R",
    "simulation/code/main_spd.R", "simulation/code/main_spd.R",
    "simulation/code/main_sphere.R", "simulation/code/main_sphere.R",
    "simulation/code/curve_spd.R", "simulation/code/curve_sphere.R",
    "simulation/code/main_sphere.R", "simulation/code/main_sphere.R",
    "simulation/code/main_sphere.R", "simulation/code/main_sphere.R"
  ),
  settings = c(
    'scenario="Swiss3", setting=2, snr=4, method="LogEuclidean", n1=100, NN=8000, n3=1000',
    'scenario="Swiss3", kappa=5, sigma=0.25, n1=100, NN=8000, n3=1000',
    'scenario="Swiss4", setting=2, snr=4, method="LogEuclidean", n1=200, NN=8000, n3=1000',
    'scenario="Swiss4", kappa=5, sigma=0.25, n1=200, NN=8000, n3=1000',
    'scenario="Swiss", setting=2, snr=2, method="LogCholesky", n1=100, NN=8000, n3=1000',
    'scenario="Swiss", setting=2, snr=4, method="LogCholesky", n1=100, NN=8000, n3=1000',
    'scenario="Swiss2", setting=2, snr=2, method="LogCholesky", n1=200, NN=8000, n3=1000',
    'scenario="Swiss2", setting=2, snr=4, method="LogCholesky", n1=200, NN=8000, n3=1000',
    'scenario="Swiss2", setting=1, snr=2, method="LogEuclidean", n1=200, n2=3000, n3=1000',
    'scenario="Swiss2", kappa=0, sigma=0.25, n1=200, n2=3000, n3=1000',
    'scenario="Swiss2", setting=1, snr=2, method="LogEuclidean", unlabeled n1=3000, labeled NN=1500, n3=1000',
    'scenario="Swiss2", kappa=0, sigma=0.25, unlabeled n1=3000, labeled NN=1500, n3=1000',
    'scenario="Swiss2", setting=4, snr=2, method="LogEuclidean", unlabeled n1=3000, labeled NN=1500, n3=1000',
    'scenario="Swiss5", setting=3, snr=2, method="LogEuclidean", n1=200, NN=8000, n3=1000',
    'scenario="Swiss5", setting=3, snr=4, method="LogEuclidean", n1=200, NN=8000, n3=1000',
    'scenario="Swiss5", kappa=0, sigma=0.25, n1=200, NN=8000, n3=1000',
    'scenario="Swiss5", kappa=5, sigma=0.25, n1=200, NN=8000, n3=1000',
    'Curve setting, snr=2, n1=100, NN=8000, n3=1000',
    'Curve setting, kappa=0, sigma=0.25, n1=100, NN=8000, n3=1000',
    'scenario="Swiss", kappa=0, sigma=0.25, n1=100, NN=8000, n3=1000',
    'scenario="Swiss", kappa=5, sigma=0.25, n1=100, NN=8000, n3=1000',
    'scenario="Swiss2", kappa=0, sigma=0.25, n1=200, NN=8000, n3=1000',
    'scenario="Swiss2", kappa=5, sigma=0.25, n1=200, NN=8000, n3=1000'
  ),
  saved_result = c(
    "spd-100-8000-1000-Swiss3-setting2-snr_4.csv",
    "sphere-100-8000-1000-Swiss3-setting2_0.25.csv",
    "spd-200-8000-1000-Swiss4-setting2-snr_4.csv",
    "sphere-200-8000-1000-Swiss4-setting2_0.25.csv",
    "spd-100-8000-1000-Swiss-setting2-snr_2_logcholesky.csv",
    "spd-100-8000-1000-Swiss-setting2-snr_4_logcholesky.csv",
    "spd-200-8000-1000-Swiss2-setting2-snr_2_logcholesky.csv",
    "spd-200-8000-1000-Swiss2-setting2-snr_4_logcholesky.csv",
    "spd-200-3000-1000-Swiss2-setting1_snr_2_r_impaction.csv",
    "sphere-200-3000-1000-Swiss2-setting1_0.25_r_impaction.csv",
    "spd-1200-3000-1000-Swiss2-setting1-snr_2_rate.csv",
    "sphere-1200-3000-1000-Swiss2-setting1_0.25_rate.csv",
    "spd-1200-3000-1000-Swiss2-setting4-snr_2_rate.csv",
    "spd-200-8000-1000-Swiss5-setting3-snr_2.csv",
    "spd-200-8000-1000-Swiss5-setting3-snr_4.csv",
    "sphere-200-8000-1000-Swiss5-setting1_0.25.csv",
    "sphere-200-8000-1000-Swiss5-setting2_0.25.csv",
    "spd-100-8000-1000-Curve-snr_2.csv",
    "sphere-100-8000-1000-Curve-0.25.csv",
    "sphere-100-8000-1000-Swiss-setting1_0.25.csv",
    "sphere-100-8000-1000-Swiss-setting2_0.25.csv",
    "sphere-200-8000-1000-Swiss2-setting1_0.25.csv",
    "sphere-200-8000-1000-Swiss2-setting2_0.25.csv"
  ),
  stringsAsFactors = FALSE
)

supplementary_simulation_map
```

# Regenerating figures from saved CSV files

The plotting scripts in `simulation/plot/` read CSV files and write figure files using the manuscript plotting style. If a plotting script contains a filename near the top of the file, set it to the target CSV before sourcing the script.

Optional examples:

```{r regenerate-simulation-plots, eval=FALSE}
old_dir <- getwd()

# plot_main.R: line charts for Figures 2, 3, S.1-S.4, S.9, S.10, S.12, and S.13.
setwd(sim_results)
source(file.path(sim_plot, "plot_main.R"))

# plot_radius.R: graph-radius curves for Figure 4(a) and Figure S.5.
setwd(sim_results)
source(file.path(sim_plot, "plot_radius.R"))

# plot_rate.R: log(AMSE)-log(n) curves for Figure 4(b) and Figures S.6-S.8.
setwd(sim_results)
source(file.path(sim_plot, "plot_rate.R"))

# plot_curve.R: oracle-comparison curves for Figure 4(d) and Figure S.11.
setwd(sim_results)
source(file.path(sim_plot, "plot_curve.R"))

setwd(old_dir)
```

# Rerunning simulations

The following chunks are set to `eval=FALSE` because the simulations are computationally intensive. Before running them, check the parameter settings listed in the tables above and in the header of each script.

```{r rerun-main-spd, eval=FALSE}
old_dir <- getwd()
setwd(sim_code)

# main_spd.R runs the SPD-matrix response simulations:
# Figures 2 and 3; Figure 4(c); Figures S.1(a), S.2(a), S.3, S.4, and S.9.
source("main_spd.R")

setwd(old_dir)
```

```{r rerun-main-sphere, eval=FALSE}
old_dir <- getwd()
setwd(sim_code)

# main_sphere.R runs the spherical-response simulations:
# Figures S.1(b), S.2(b), S.10, S.12, and S.13.
source("main_sphere.R")

setwd(old_dir)
```

```{r rerun-radius-experiments, eval=FALSE}
old_dir <- getwd()
setwd(sim_code)

# radius_spd.R runs the SPD graph-radius experiment for Figure 4(a) and Figure S.5(a).
source("radius_spd.R")

# radius_sphere.R runs the spherical graph-radius experiment for Figure S.5(b).
source("radius_sphere.R")

setwd(old_dir)
```

```{r rerun-rate-experiments, eval=FALSE}
old_dir <- getwd()
setwd(sim_code)

# rate_spd.R runs the SPD empirical-rate experiments for Figure 4(b) and Figures S.6 and S.8.
source("rate_spd.R")

# rate_sphere.R runs the spherical empirical-rate experiment for Figure S.7.
source("rate_sphere.R")

setwd(old_dir)
```

```{r rerun-curve-experiments, eval=FALSE}
old_dir <- getwd()
setwd(sim_code)

# curve_spd.R runs the SPD oracle-comparison experiment for Figure 4(d) and Figure S.11(a).
source("curve_spd.R")

# curve_sphere.R runs the spherical oracle-comparison experiment for Figure S.11(b).
source("curve_sphere.R")

setwd(old_dir)
```

# Session information

The saved real data results were generated using R version 4.5.0. The following output records the R environment used to render this document.

```{r session-info}
sessionInfo()
```
